---
title: "Biophysics and Imaging Subgroup Statistics"
date: "Updated: `r format(Sys.time(),format = '%A, %B %d, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
---

<style>
    body .main-container {
        max-width: 4000px;
    }
</style>

```{r, include=FALSE, results='asis'}
library('dplyr')
library('tidyr')
library('ggplot2')
library('knitr')
library('kableExtra')

#wednesday date range 1
date.start.wed = '170125'
date.end.wed = '171011'

#thursday date range
date.start.thurs = '171019'
date.end.thurs = '171214'

#wednesday date range 2 - current range
date.start.wed2 = '171220'
date.end.wed2 = format(Sys.time(),format = '%y%m%d')


figsize = 5
timefigscale = 2/3 #number of inches per bar 
textsize = 12
options(width = 12)

datefmtstr = "%y%m%d"
#Make the first set of Wednesday dates
dates.wed = format(seq(as.Date(date.start.wed,datefmtstr),as.Date(date.end.wed,datefmtstr),by = "week"), format = datefmtstr)  
#Make the first set of Thursday dates
dates.thurs = format(seq(as.Date(date.start.thurs,datefmtstr),as.Date(date.end.thurs,datefmtstr),by = "week"), format = datefmtstr)
#Make the second set of Wednesday dates - active set
dates.wed2 = format(seq(as.Date(date.start.wed2,datefmtstr),as.Date(date.end.wed2,datefmtstr),by = "week"), format = datefmtstr)

dates = c(dates.wed,dates.thurs,dates.wed2) #put them all together 

times = read.table(file = paste0("Subgroup Stats/",dates[1],"_data.csv"),header = TRUE,stringsAsFactors=FALSE,sep = ",")
misdates = "Missing: ";

for (i in 2:length(dates)) {
  filename = paste0("Subgroup Stats/",dates[i],"_data.csv")
  if(file.exists(filename)) {
    temp = read.table(file = filename,header = TRUE,stringsAsFactors=FALSE,sep = ",")
    times = bind_rows(times,temp)
  } else {
    misdates = paste0(misdates," ",format(as.Date(dates[i],datefmtstr), format = "%m/%d/%Y"))
  }
}

#names.avg = times %>% group_by(name) %>% summarise_each(funs(median)) %>% select(-date) %>% mutate(time = time/60)
#names.avg$name = factor(names.avg$name, levels = names.avg$name[order(names.avg$time)], ordered = TRUE)

nsubgroups = length(unique(times$date))

names.n = times %>% select(name,date) %>% group_by(name) %>% summarise_all(funs(dplyr::n_distinct)) %>% select(name,n = date)

names.avg = times %>% mutate(time = time/60) %>% select(-date,-order) %>% group_by(name) %>% summarise_all(funs(median, mean, sd)) %>% 
  left_join(names.n, by = "name")
names.avg$name = factor(names.avg$name, levels = names.avg$name[order(names.avg$median, names.avg$mean)], ordered = TRUE)
names.avg = names.avg %>% mutate(diff = median-mean, nper = (n / nsubgroups * 100)) %>% select(name,median,mean,diff,sd,n,nper)

pos.avg = times %>% select(-name,-date) %>% group_by(order) %>% summarise_each(funs(mean)) %>% mutate(time = time/60)
pos.std = times %>% select(-name,-date) %>% group_by(order) %>% summarise_each(funs(sd))  %>% mutate(tstd = time/60) %>% select(order,tstd)
pos.avg = left_join(pos.avg,pos.std, by = 'order')

group.avg = times %>% mutate(time = time/60) %>% select(time) %>% summarise_all(funs(median, mean, sd)) %>% 
  mutate(n = nsubgroups, name = "Total") %>% 
  mutate(diff = median-mean, nper = (n / nsubgroups * 100)) %>% select(name,median,mean,diff,sd,n,nper)


times2 = times %>% mutate(time = time/60)
times2$name = factor(times2$name, levels = names.avg$name[order(names.avg$median, names.avg$mean)], ordered = TRUE)

times3 = times2
times3$order = factor(times3$order)

times4 = times2[order(times2$date,times2$order),]
times4$date = factor(times4$date)
tempdate = as.Date(times4$date,datefmtstr)
times4$date = format(tempdate, format = "%m/%d/%Y")

times5 = times2 %>% select(-name) %>% group_by(date) %>% summarise(time = sum(time), attend = max(order)) %>% 
  ungroup() %>% mutate(tpera = time / attend)
maxattendees = max(times5$attend)
medtime = times5 %>% group_by(attend) %>% summarise(time = median(time)) %>% ungroup()
timefit = lm(times5$time ~ times5$attend)
timecoeff = timefit$coefficients
attend = 0:(maxattendees)
fitplot = timecoeff[1]+timecoeff[2]*attend
fitframe = data.frame(attend,fitplot)
times5.f = times5
fitframe.f = fitframe
times5.f$attend = factor(times5.f$attend)
fitframe.f$attend = factor(fitframe.f$attend)

avgtimeperperson = mean(times5$tpera)
names = names.avg$name
meandiff = rep(0,times = length(names))

for (i in 1:length(names)) {
  presentdays = times2 %>% select(name,date) %>% filter(name == names[i])
  presentnumbers = inner_join(presentdays,times5, by = 'date')
  meandiff[i] = mean(presentnumbers$tpera) - avgtimeperperson
}
meandiff = 60*meandiff
meandiff.f = data.frame(names,meandiff)

titlestr = paste0("Subgroup from ",format(as.Date(dates[1],datefmtstr), format = "%m/%d/%Y"),
                  " to ",format(as.Date(tail(dates, n=1),datefmtstr), format = "%m/%d/%Y"))

plottheme = theme_bw() + theme(text = element_text(size = textsize, family = "ArialMT"), 
                               panel.grid.major.x = element_blank(), panel.grid.major.y = element_line(color = 'grey75', size = 0.25),
                               panel.grid.minor.y = element_line(color = 'grey85', size = 0.25), 
                               panel.border = element_rect(fill = NA, color = 'black', size = 0.75),
                               legend.title = element_blank(), legend.key = element_blank())  

astart = 260
aspace = 12.5
ax = 1
ncorr = format(round(cor(times5$attend,times5$time), 4), nsmall = 4)

```
## Summary

`r titlestr` for a total of `r nsubgroups` subgroup meetings.    

`r misdates`   

```{r, key, echo=FALSE}
secondsToString <- function(x,digits=2){
   unlist(
      lapply(x,
         function(i){
            # fractional seconds
            fs <- as.integer(round((i - round(i))*(10^digits)))
            fmt <- ''
            if (i >= 3600)
               fmt <- '%H:%M:%S'
            else if (i >= 60)
            fmt <- '%M:%S'
            else
               fmt <- '%OS'

            i <- format(as.POSIXct(strptime("0:0:0","%H:%M:%S")) + i, format=fmt)
            if (fs > 0)
               sub('[0]+$','',paste(i,fs,sep='.'))
            else
               i
         }
      )
   )
}

med.table = names.avg[order(names.avg$name),] 
med.table$name = as.character(med.table$name)
med.table = bind_rows(med.table,group.avg) %>% mutate(rank = c( as.character(seq(1,nrow(names.avg))), " " )) %>% 
  select(rank,name,median,mean,diff,sd,n,nper)

#med.table$mean = secondsToString(med.table$mean*60,digits = 0)
#med.table$median = secondsToString(med.table$median*60,digits = 0)
#med.table$diff = med.table$diff*60
#med.table$sd = secondsToString(med.table$sd*60,digits = 0)
kable(med.table,"html",col.names = c(" "," ", "Median", "Mean", "Median - Mean", "Standard Deviation", "Count", "Percent"), 
      row.names = FALSE, digits = 2)  %>% kable_styling(bootstrap_options = c("striped", "hover"), full_width = F, position = "left") %>% 
  add_header_above(c(" ", "  ", "Time (min)" = 4, "Attendance" = 2)) %>% row_spec(nrow(names.avg)+1, bold = T, background = "#BBBBBB")
```


## Length per day
### Stacked bar
```{r, fig.width=20, fig.height=6, echo=FALSE}
ggplot(times4,aes(date,time)) + 
  geom_bar(aes(fill = name, group = order), stat = "identity", color = 'black', position = position_stack(reverse = TRUE)) + scale_fill_brewer(palette = "Set1") +
  ylab('time (min)') + xlab(NULL) + scale_y_continuous(expand = c(0,0), limits = c(0,270), breaks = c(0,60,120,180,240,270)) + 
  plottheme +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
    
Bars are in speaking order from bottom (time 0) to top (end). 

### Offset bar
```{r, fig.width=20, fig.height=6, echo=FALSE}
filtweek = 8
filtdates = presentdays$date
filtdates = filtdates[(length(filtdates)-filtweek+1):length(filtdates)]

ggplot(times4,aes(date,time)) + 
  geom_bar(aes(fill = name, group = order), stat = "identity", color = 'black', position = position_dodge()) + 
  scale_fill_brewer(palette = "Set1") +
  ylab('time (min)') + xlab(NULL) + scale_y_continuous(expand = c(0,0), limits = c(0,120), breaks = c(0,15,30,45,60,75,90,105,120)) + 
  plottheme +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
     
Same as above except each person is side by side to compare total times. 

## Time per person
### Box plot
```{r, fig.width=6, fig.height=4, echo=FALSE}
ggplot(times2,aes(name,time)) + 
  geom_boxplot(aes(fill = name)) + scale_fill_brewer(palette = "Set1", guide = FALSE) + plottheme + 
  ylab('time (min)') + xlab(NULL)
```

Boxes are ordered by the median speaking time (black bar in the box plot).
Lower and upper box edges correspond to the first and third quartiles. Whiskers extend to no more than the 1.5 times the interquartile range. Individual points are outliers beyond the whiskers. 

### Scatter plot
```{r, fig.width=6, fig.height=4, echo=FALSE}
ggplot(times2,aes(name,time)) + 
  geom_point(aes(fill = factor(order)), size = 2, shape = 21, color = 'black') + scale_fill_brewer(palette = "Blues") + plottheme + 
  ylab('time (min)') + xlab(NULL)
```


## Time compared to order
### Box plot
```{r, fig.width=6, fig.height=4, echo=FALSE}
ggplot(times3,aes(order,time)) + 
  geom_boxplot(aes(fill = order)) +  plottheme + scale_fill_brewer(palette = "Blues") +
  ylab('time (min)') + xlab('order position')
```


### Scatter plot
```{r, fig.width=6, fig.height=4, echo=FALSE}
ggplot(times2,aes(order,time)) + 
  geom_point(aes(fill = name), size = 2, shape = 21, color = 'black') + scale_fill_brewer(palette = "Set1") + plottheme + 
  ylab('time (min)') + xlab('order position')
```

Each point corresponds to a person's speaking time at the speaking order. 

## Time per number of people scatter plot
```{r, fig.width=6, fig.height=4, echo=FALSE}
ggplot(times5,aes(attend,time)) + 
  geom_point(fill = "white") +  plottheme + scale_y_continuous(expand = c(0,0), limits = c(0,270), breaks = c(0,60,120,180,240,270)) +
  geom_line(data = fitframe, aes(attend,fitplot, group = 1)) +
  annotate('text', label = paste0("Slope: ", format(round(timecoeff[2], 2), nsmall = 2), " min"), x = ax, y = astart) +
  annotate('text', label = paste0("Intercept: ", format(round(timecoeff[1], 2), nsmall = 2), " min"), x = ax, y = astart-aspace) +
  annotate('text', label = paste0("R: ", ncorr), x = ax, y = astart-2*aspace) +
  ylab('time (min)') + xlab('number of people')
```



## How often each person goes in an order position
```{r, fig.width=6, fig.height=6, echo=FALSE}
plot <- ggplot(times2,aes(x = order)) + 
  geom_histogram(aes(y = ..count.., fill = name), color = 'black', binwidth = 1) + plottheme +
  ylab('counts') + xlab('order position') + facet_wrap(~ name, ncol = 3, scales = "fixed") +
  scale_x_continuous(breaks = 1:nrow(names.avg)) + scale_fill_brewer(palette = "Set1", guide = FALSE)
maxcount <- max(ggplot_build(plot)$data[[1]]$count)
plot + scale_y_continuous(breaks = seq(from = 0, to = maxcount, by = 2)) 
```



<!-- ## Time difference when person is present -->
```{r, fig.width=6, fig.height=4, include=FALSE}
ggplot(meandiff.f,aes(names,meandiff)) + 
  geom_bar(aes(fill = names), stat = "identity", color = 'black') + scale_fill_brewer(palette = "Set1", guide = FALSE) + plottheme + 
  ylab('time per person change (s)') + xlab(NULL) + 
  scale_y_continuous(expand = c(0,0), limits = c(-120,30), breaks = c(-120,-90,-60,-30,0,30))
```